
		\begincal
		\monthtext{Januari}
		\daytext{1}
		\quotestart
		\quote{Obama said, "Yes we can." Chuck Norris says, "I already did.".}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{2}
		\quotestart
		\quote{God created a flood to punish the world....now..its Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{3}
		\quotestart
		\quote{A blanket uses Chuck Norris to stay warm.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris doesn't need a miracle in order to split the ocean. He just walks in and the water gets out of the way.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{5}
		\quotestart
		\quote{There are two types of people in this world: Chuck Norris and the rest.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{6}
		\quotestart
		\quote{The opening scene of the movie "Saving Private Ryan" is loosely based on games of dodgeball Chuck Norris played in second grade.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris once robbed a gun store with a knife.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris invented Kentucky Fried Chicken's famous secret recipe, with eleven herbs and spices. But nobody ever mentions the twelfth ingredient: Fear.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{9}
		\quotestart
		\quote{When Chuck Norris throws a rock at night, it is known as a shooting star.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{10}
		\quotestart
		\quote{Chuck Norris does not submit to homeland security, he IS homeland security.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris can paste before he copies.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris knows letters before A.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{13}
		\quotestart
		\quote{The Pope confesses to Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{14}
		\quotestart
		\quote{Chuck Norris can sneeze with his eyes open.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{15}
		\quotestart
		\quote{Chuck Norris' blood type is unknown. He has never bled.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris does not know where you live, but he knows where you will die.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{17}
		\quotestart
		\quote{Someone once tried to tell Chuck Norris that roundhouse kicks aren't the best way to kick someone. This has been recorded by historians as the worst mistake anyone has ever made.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can run you over with a parked car.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris can tear a facebook page.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{20}
		\quotestart
		\quote{For acne problems you can use proactiv or have Chuck Norris round house kick it off your face.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{21}
		\quotestart
		\quote{In 1991, Chuck Norris shot a 14 on an 18 hole golf course, falling short of his personal best by 2 strokes.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{22}
		\quotestart
		\quote{All men are created equal.....except for Chuck Norris, he's better}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris can play the violin with a piano}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris doesn't look in the closet for the boogey man. The boogey man looks in the closet for Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris has the greatest Poker-Face of all time. He won the 1983 World Series of Poker, despite holding only a Joker, a Get out of Jail Free Monopoloy card, a 2 of clubs, 7 of spades and a green \#4 card from the game UNO.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{26}
		\quotestart
		\quote{Chuck Norris' grenade has a silencer.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{27}
		\quotestart
		\quote{Chuck Norris once found a hay in a needlestack.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{28}
		\quotestart
		\quote{Scientists have estimated that the energy given off during the Big Bang is roughly equal to 1CNRhK (Chuck Norris Roundhouse Kick)}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{29}
		\quotestart
		\quote{When a zombie apocalypse starts, Chuck Norris doesn't try to survive. The zombies do.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{30}
		\quotestart
		\quote{Yoda took lessons from Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Januari}
		\daytext{31}
		\quotestart
		\quote{When Chuck Norris crosses the steet the cars have to look both ways.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{1}
		\quotestart
		\quote{Chuck Norris wasnt created. He made himself.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{2}
		\quotestart
		\quote{Chunk Norris can rip a page out of facebook.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris can beat scissors with paper.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{4}
		\quotestart
		\quote{Someone once gave Chuck Norris the finger.....he still has it.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris can roll a seven with one die.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris can breathe under water because water is to scared to invade his airspace.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris stole the cookie from the cookie jar...and if you value your life, you'll let him eat in peace.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris sucks blood from a vampire.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{9}
		\quotestart
		\quote{When you ask Chuck Norris for an autograph, he pours ink on his boot and roundhouse kicks you in the face.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{10}
		\quotestart
		\quote{Sigmund Freud was talking to Chuck Norris about his theories of psychology. Withoit thinking, Freud asked Chuck Norris if he was afraid of anything. Chuck Norris looked at him and said, "Excuse me???" Thus the term "Fruedian Slip" became a psychological term.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{11}
		\quotestart
		\quote{The only sport Chuck Norris would score lower than you in is golf.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris does not throw grenades, he Chucks them.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{13}
		\quotestart
		\quote{When Steven Hawking saw Chuck Norris coming his way, he got up and ran for shelter.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{14}
		\quotestart
		\quote{Chuck Norris got Coronavirus. Now the Coronavirus is in isolation.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{15}
		\quotestart
		\quote{Heights are afraid of Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris is the only person that can punch a cyclops between the eye.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{17}
		\quotestart
		\quote{If Chuck Norris added you on Facebook, you dont have a choice if you want to accept or not.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{18}
		\quotestart
		\quote{If Chuck Norris had a nickel for every time he heard a Chuck Norris joke, he would have zero nickels. No one jokes about Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris roundhouse kicked a rabbit so hard it crapped an egg. Hence, Easter exists.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{20}
		\quotestart
		\quote{What was going through the minds of all of Chuck Norris' victims before they died? His shoe.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{21}
		\quotestart
		\quote{Even gravity can't defy Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{22}
		\quotestart
		\quote{Chuck Norris can turbocharge an electric car.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris can single-handedly surround his opponents.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris walked into a bar. The bar said "ouch".}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris was born in a log cabin built by his own two hands.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{26}
		\quotestart
		\quote{Superheros read Chuck Norris comics.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{27}
		\quotestart
		\quote{Ghosts sit around campfire and tell Chuck Norris stories.}
		\endcal

		\begincal
		\monthtext{Februari}
		\daytext{28}
		\quotestart
		\quote{Using Chuck Norris in a war is a violation of human rights.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{1}
		\quotestart
		\quote{In space Chuck Norris can hear you scream.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris was born on Febuary 30th. Thats why Febuary 30th doesn't come around to often.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris once fought superman. The loser had to wear his underwear over his pants.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris once smoked a cigarette, but he didn't get addicted to smoking. The cigarette got addicted to Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris can hear sign language.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris shushes the librarian.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris never buys an extended warranty, he dares his purchase to fail.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris uses a shotgun for a blow dryer.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{9}
		\quotestart
		\quote{Chuck Norris was asked to play a wood instrument in the school band. He showed up with a baseball bat and asked, "So who's first?".}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{10}
		\quotestart
		\quote{Queens have a Chuck Norris size bed.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris doesn't make chocolate milk, he tells his cow to.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris can squeeze orange juice out of a lemon}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{13}
		\quotestart
		\quote{Chuck Norris once punched a man back into a monkey. Therefore proving evolution at the same time.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{14}
		\quotestart
		\quote{Usain Bolt can run 44.72 km/h, Chuck Norris is the camera man running beside him.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{15}
		\quotestart
		\quote{Chuck Norris has a vacation home on the sun.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris can go right and left at the same time.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{17}
		\quotestart
		\quote{Chuck Norris doesn't have a chin. he just has another fist.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris could set every record, but he feels it would be to easy.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{19}
		\quotestart
		\quote{As a kid, Chuck Norris made his dad go to his room.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{20}
		\quotestart
		\quote{Life is too scared to give Chuck Norris lemons.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris's favorite toy as a kid was a Chuck Norris action figure.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{22}
		\quotestart
		\quote{Saying "Chuck Norris" after your opponent says "Check Mate" in the game of Chess, instantly makes you the winner.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris doesn't get the wrong answer, you ask the wrong question.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris won the world's longest handstand competition with his hands tied behind his back.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{25}
		\quotestart
		\quote{When the Boogeyman goes to sleep every night he checks his closet for Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{26}
		\quotestart
		\quote{Mistakes learn from Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{27}
		\quotestart
		\quote{Chuck Norris can speak braille.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{28}
		\quotestart
		\quote{It takes Chuck Norris 20 minutes to watch 60 Minutes.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{29}
		\quotestart
		\quote{When Chuck Norris looks in the mirror nothing appears. There can never be a second Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris can make hell freeze over.}
		\endcal

		\begincal
		\monthtext{Maart}
		\daytext{31}
		\quotestart
		\quote{Chuck Norris used to beat the shit out of his shadow because it was following to close. It now stands a safe 30 feet behind him.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{1}
		\quotestart
		\quote{Sorry, deze dag is te serieus voor grappen.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris can draw a perfect circle. With a ruler.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris can pull a hat out of a rabbit.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{4}
		\quotestart
		\quote{When Chuck Norris plays horse shoes the horse is still wearing them.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{5}
		\quotestart
		\quote{In fine print on the last page of the Guinness Book of World Records it notes that all world records are held by Chuck Norris, and those listed in the book are simply the closest anyone else has ever gotten.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris has brail on his boots so even blind people know when it's coming.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris plays Battleship with a real navy.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris dared the red sea to stay whole.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{9}
		\quotestart
		\quote{When you enter Chuck Norris into a GPS it says "behind you".}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{10}
		\quotestart
		\quote{Chuck Norris did a round house kick so hard he went back in time to stop the bullet that killed President Kennedy, but in amazement Kennedy's head exploded.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{11}
		\quotestart
		\quote{Thunderstorms occur when Chuck Norris eats Mexican Food.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris' longest attempt at holding his breath was measured on a calender.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{13}
		\quotestart
		\quote{Chuck Norris' dryer doesnt steal one sock. It gives him one extra.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{14}
		\quotestart
		\quote{People get hit by cars. Cars get hit by Chuck Norris.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{15}
		\quotestart
		\quote{Chuck Norris doesn't walk forward. The earth rotates backwards.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris can knit the softest sweater using electrical pylons.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{17}
		\quotestart
		\quote{If Hurricane Chuck Norris ever came, earth would Explode and everything would die. Expect Chuck Norris.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris eats habanero peppers to cool down on a hot day.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris was the first man to walk on a man on the moon.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{20}
		\quotestart
		\quote{Chuck Norris once hit a home run with an uncooked spaghetti noodle.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris''' hand is the only hand that can beat a Royal Flush.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{22}
		\quotestart
		\quote{When Chuck Norris does push-ups, he doesn't push himself up, he pushes the earth down.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris is the only person on the planet that can kick you in the back of the face.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris once ate an entire bottle of sleeping pills. They made him blink.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{25}
		\quotestart
		\quote{The Internet uses Chuck Norris for information.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{26}
		\quotestart
		\quote{What happened to all the dinosaurs? Chuck Norris}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{27}
		\quotestart
		\quote{When Chuck Norris enters a room, he doesn't turn the lights on, he turns the dark off.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{28}
		\quotestart
		\quote{An officer once stopped Chuck Norris, the officer left with a warning.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{29}
		\quotestart
		\quote{God listed Chuck Norris as his emergency contact person.}
		\endcal

		\begincal
		\monthtext{April}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris invented the laws of physics just so he could break them.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{1}
		\quotestart
		\quote{Chuck Norris donates his chest hair to make steel wool.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{2}
		\quotestart
		\quote{The second world war ended when Chuck Norris got bored.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris once robbed himself and doubled his profit.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris can walk across the North/South Korean border.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris does not use a parachute when he jumps out of an airplane. They only slow him down.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{6}
		\quotestart
		\quote{If you cut open the Earth, you would find "Made By Chuck Norris" inscribed on the core.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{7}
		\quotestart
		\quote{When life gives Chuck Norris lemons, Chuck Norris makes apple sauce.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris is so fast that he turned off the light in his bedroom, and was in bed before the room got dark.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{9}
		\quotestart
		\quote{When Chuck Norris throws a boomerang, it doesn't come back.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{10}
		\quotestart
		\quote{The only reason aliens don't invade is because they're waiting for Chuck Norris to die.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris can only punch you in the face once, because the second time you wont have a face.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris once punched a man in the soul.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{13}
		\quotestart
		\quote{Theres no LIVING rooms in Chuck Norris' house.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{14}
		\quotestart
		\quote{Chuck Norris doesn't help people, he just doesn't kill them that day.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{15}
		\quotestart
		\quote{Norrisaphobia- The extreme fear of being roundhouse kicked in the face.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{16}
		\quotestart
		\quote{The First Law of Thermodynamics states that energy can neither be created nor destroyed... unless it meets Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{17}
		\quotestart
		\quote{Chuck Norris fell off of the Empire State building and stubbed his toe.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can burn calories with a flamethrower.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{19}
		\quotestart
		\quote{There once was a street called Chuck Norris, but the name was changed for public safety because nobody crosses Chuck Norris and lives.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{20}
		\quotestart
		\quote{Chuck Norris has a blood pressure reading of zero over zero. Chuck Norris has never felt any pressure.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris was once charged with three attempted murders in Boulder County, but the Judge quickly dropped the charges because Chuck Norris does not "attempt" murder.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{22}
		\quotestart
		\quote{If you cut off Chuck Norris' arm it will grow back...and the arm you cut off will grow another Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris was once run over by a tank. He refused to pay for it.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris has broken the land speed record riding a bike with no chain and a flat tire.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris can hit you so hard that he can actually alter your DNA. Decades from now your descendants will occasionally clutch their heads and yell "What The Hell was That?"}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{26}
		\quotestart
		\quote{What do you find when you go to the end of the universe? Chuck Norris}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{27}
		\quotestart
		\quote{Chuck Norris looks in the mirror for backup.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{28}
		\quotestart
		\quote{The reason nobody is aloud to go to area 51 is simply because Chuck Norris doesn't want any body in or around his house.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{29}
		\quotestart
		\quote{Scholars believe that the only thing capable of making Chuck Norris cry is a picture of himself crying. Such a picture does not exist.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris can speak French... In Russian.}
		\endcal

		\begincal
		\monthtext{Mei}
		\daytext{31}
		\quotestart
		\quote{The IRS pays Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{1}
		\quotestart
		\quote{The last thing Chuck Norris wants to do is hurt you, and it's also the first.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris can make your blue eyes black}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{3}
		\quotestart
		\quote{It takes Chuck Norris a half an hour to watch 60 Minutes.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{4}
		\quotestart
		\quote{Once, while Chuck Norris was tanning, there was a lunar eclipse. That's why the moon has dints in it.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris can unring a bell.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{6}
		\quotestart
		\quote{When life gives Chuck Norris lemons, he returns them for a refund.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris doesn't lie. He simply changes the truth.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris is the only man to ever defeat a brick wall in a game of tennis.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{9}
		\quotestart
		\quote{Chuck Norris knows who anonymous is.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{10}
		\quotestart
		\quote{If it looks like chicken, tastes like chicken, and feels like chicken but Chuck Norris says its beef, then it's beef.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris plays horseshoes with horses still attached to them.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{12}
		\quotestart
		\quote{There was finally a WMD in Iraq when Chuck Norris visited the troops.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{13}
		\quotestart
		\quote{People don't tell Chuck Norris jokes, they simply tell his life story.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{14}
		\quotestart
		\quote{How many push-ups can Chuck Norris do? Answer: All of them!}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{15}
		\quotestart
		\quote{A police officer once pulled over Chuck Norris. The police officer was lucky to leave with just a warning.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris simply walks into mordor.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{17}
		\quotestart
		\quote{Chuck Norris can drown a fish.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris is the reason Waldo is hiding.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris can skip the copyright notices on his DVDs.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{20}
		\quotestart
		\quote{Chuck Norris can erase permanent marker.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{21}
		\quotestart
		\quote{Ghosts are actually caused by Chuck Norris killing people faster than Death can process them.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{22}
		\quotestart
		\quote{9-1-1 calls Chuck Norris for an Emergency.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris doesn't shower, he only takes blood baths.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{24}
		\quotestart
		\quote{The shortest distance between two points is whatever route Chuck takes.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris once felt fear. Then he roundhouse kicked the mirror.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{26}
		\quotestart
		\quote{Chuck Norris once went to a magic show. The magician asked for a volunteer for his disappearing act. Chuck Norris raised his hand and the magician disappeared.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{27}
		\quotestart
		\quote{A Chuck Norris a day keeps the enemies away.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{28}
		\quotestart
		\quote{Chuck Norris doesn't fight wars. He settles them.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{29}
		\quotestart
		\quote{Chuck Norris can perform plastic surgery with his bare hands.}
		\endcal

		\begincal
		\monthtext{Juni}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris was once hit by a bus. A lot of people died that day..}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{1}
		\quotestart
		\quote{Santa Claus sits on Chuck Norris' lap.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris can break a ghosts leg.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{3}
		\quotestart
		\quote{When Chuck Norris was in middle school, his English teacher assigned an essay: "What is courage?" He received an A+ for turning in a blank page with only his name at the top.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{4}
		\quotestart
		\quote{If you've ever wanted to see an unstoppable force meet an immovable object, just watch Chuck Norris punch himself.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{5}
		\quotestart
		\quote{Cuck Norris killed the dead sea.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris keeps 45\% of the worlds medical staff employed.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris made his first paper airplane when he was 4 years old..... it landed yesterday.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{8}
		\quotestart
		\quote{The last digit of pi is Chuck Norris. He is the end of all things.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{9}
		\quotestart
		\quote{The reason newborn babies cry is because they know they have just entered a world with Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{10}
		\quotestart
		\quote{Chuck Norris is never early. Time just can't keep up with Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris can run over a tank with his bicycle.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{12}
		\quotestart
		\quote{The reason the Holy Grail has never been recovered is because nobody is brave enough to ask Chuck Norris to give up his favourite coffee mug.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{13}
		\quotestart
		\quote{Chuck Norris ended the "Never Ending Story".}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{14}
		\quotestart
		\quote{Chuck Norris plays russian roulette with a fully loded revolver... and wins.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{15}
		\quotestart
		\quote{Zeus is the Greek God of thunder. Chuck Norris is the Greek God of Zeus.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{16}
		\quotestart
		\quote{James Cameron wanted Chuck Norris to play the Terminator. However, upon reflection, he realized that would have turned his movie into a documentary, so he went with Arnold Schwarzenegger.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{17}
		\quotestart
		\quote{The quickest way to a man's heart is with Chuck Norris' fist.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can hit the bottom of a bottomless pit.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris uses tear gas for air freshener.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{20}
		\quotestart
		\quote{Chuck Norris can play Beethoven's Symphony \#9 on the bongos.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris eats the core of an apple first.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{22}
		\quotestart
		\quote{Chuck Norris made Atlantis sink.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris' beard can roundhouse kick you.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris has eyes in the back of YOUR head.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris biggest idol is his mirror, because it dares to duplicate him.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{26}
		\quotestart
		\quote{Chuck Norris threw a grenade and killed 50 people, then it exploded.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{27}
		\quotestart
		\quote{Chuck Norris burns his bridges BEFORE he crosses them.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{28}
		\quotestart
		\quote{Chuck Norris can milk ground beef from a cow.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{29}
		\quotestart
		\quote{Chuck Norris can speak in Morse code.}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris wasn't born. He willed himself into existence.}

		\quote{Chuck Norris was old enough to vote when he was born.}

		\quote{Chuck Norris has 2 birthdays in a year.}

		\quote{On his birthday, Chuck Norris blows out his candles by blinking.}

		\quote{Gefeliciteerd Jorn!}
		\endcal

		\begincal
		\monthtext{Juli}
		\daytext{31}
		\quotestart
		\quote{Mother Teresa said Chuck Norris was the only man she ever wanted to marry.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{1}
		\quotestart
		\quote{More people are scared of spiders then death, spiders are scared of Chuck Norris}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{2}
		\quotestart
		\quote{If you say the term "Nobody's perfect." Chuck Norris takes that as an insult.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{3}
		\quotestart
		\quote{Bears have to put up "Don't feed Chuck Norris" signs.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris stepped in front of a speeding train. He was the only survivor.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris can win tic-tac-toe in one turn.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris went around the world...by standing still.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris sleeps with a pillow under his gun.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris can lead a horse to water AND make it drink.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{9}
		\quotestart
		\quote{Jack was nimble, Jack was quick, but Jack still couldn't dodge Chuck Norris' roundhouse kick.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{10}
		\quotestart
		\quote{Pinatas were made in an attempt to get Chuck Norris to stop kicking the people of Mexico. Sadly this backfired, as all it has resulted in is Chuck Norris now looking for candy after he kicks his victims.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{11}
		\quotestart
		\quote{When Chuck Norris wants an egg, he cracks open a chicken.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris can shock electricity.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{13}
		\quotestart
		\quote{Chuck Norris had 3 pets. A goldfish, a lizard, and a monkey. He put his blood in each one and we now know them as Jaws, Godzilla, and King Kong.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{14}
		\quotestart
		\quote{Kings buy Chuck Norris size beds.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{15}
		\quotestart
		\quote{If you spell Chuck Norris in Scrabble, you win. Forever.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris' submarine is a convertible.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{17}
		\quotestart
		\quote{Jesus asks himself, "What Would Chuck Norris Do?"}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris IS the original gangster.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris has cows grilling his steaks for him.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{20}
		\quotestart
		\quote{Chuck Norris wouldn't have to run for president. He could simply walk.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris clips his toenails with a chain saw.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{22}
		\quotestart
		\quote{Chuck Norris can score a touchdown in basketball.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{23}
		\quotestart
		\quote{The common people know nuclear power as an alternative energy source. Chuck Norris calls it his tanning bed.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris once asked government authorities if they wanted him to be another form of capital punishment.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris can explain what fire tastes like.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{26}
		\quotestart
		\quote{Chuck Norris CAN find the end of a circle.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{27}
		\quotestart
		\quote{The only reason lighting doesnt strike in the same place twice is because it knows Chuck is looking for it.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{28}
		\quotestart
		\quote{Chuck Norris was once asked what he felt when he shot criminals, he simply shrugged and said "Recoil".}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{29}
		\quotestart
		\quote{In the early 70's Chuck Norris and Arnold Schwarzenegger got into a fight. With just one round house kick to the face, Arnold hasn't talked the same ever since}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{30}
		\quotestart
		\quote{In front of Chuck Norris' dog's house it is written 'beware of the owner'.}
		\endcal

		\begincal
		\monthtext{Augustus}
		\daytext{31}
		\quotestart
		\quote{Chuck Norris once had parkinsons, but he shook it off.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{1}
		\quotestart
		\quote{If at first you don't succeed, you're not Chuck Norris.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris can taste lies.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{3}
		\quotestart
		\quote{Bigfoot believes in Chuck Norris. Thats why he's always hiding.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris said no more of these jokes about him...... or else}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris has a diary. It's called the Guinness Book of World Records.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris was born on February 30th.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris can squeeze blood from a stone.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{8}
		\quotestart
		\quote{When Chuck Norris gets a syntax error on a calculator he says what? Then the answer appears on the screen}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{9}
		\quotestart
		\quote{While other children were playing in sand, Chuck was playing in concrete.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{10}
		\quotestart
		\quote{When Chuck Norris robs a store, the cops are standing at the door saying ''good luck with the money''.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{11}
		\quotestart
		\quote{On the seventh day, God rested. But Chuck Norris worked out.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris never fails, he tells success to come back when its ready for him.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{13}
		\quotestart
		\quote{When you play chess with Chuck Norris, he always puts you in Chuck-mate.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{14}
		\quotestart
		\quote{Kids play jumprope. Chuck Norris plays jumpcobra.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{15}
		\quotestart
		\quote{Newtons law is wrong, there is no reaction equal to a Chuck Norris roundhouse kick.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris sleeps with a night light. Not because Chuck Norris is afraid of the dark, but the dark is afraid of Chuck Norris}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{17}
		\quotestart
		\quote{Chuck Norris once hit a dead man and brought him back to life.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can see all 6 sides of a cube at once.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris was once asked in an interview what he thought about all the Chuck Norris jokes going around. He simply said "They aren't jokes" and went back to drinking his mug of nails.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{20}
		\quotestart
		\quote{Chuck Norris makes onions cry.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris earned a lifetime achievement award in just one day.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{22}
		\quotestart
		\quote{Chuck Norris shot someone.......with a knife.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{23}
		\quotestart
		\quote{Chuck Norris is a lover not a fighter but don't get fooled he is also a fighter.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{24}
		\quotestart
		\quote{For Chuck Norris every street is one way, his way.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris can give you THREE black eyes.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{26}
		\quotestart
		\quote{Chuck Norris can breathe in space.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{27}
		\quotestart
		\quote{The following is a short list of things Chuck Norris cannot do: .}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{28}
		\quotestart
		\quote{Chuck Norris cheated on his English test............with a calculator.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{29}
		\quotestart
		\quote{Chuck Norris invented his own type of karate. It's called Chuck-Will-Kill.}
		\endcal

		\begincal
		\monthtext{September}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris can build a snowman out of rain.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{1}
		\quotestart
		\quote{Everyone who wakes up on Christmas morning gets a Christmas present from Chuck Norris. The fact that they are allowed to wake up on Christmas morning.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris can find his way around using Apple Maps.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris uses hot sauce as eye drops.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris bit the apple logo.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{5}
		\quotestart
		\quote{Chuck Norris is currently suing NBC, claiming Law and Order are trademarked names for his left and right legs.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{6}
		\quotestart
		\quote{Chuck Norris has to carry a license to bear arms...not for his guns, but for his actual arms.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris once lapped his opponent, in a drag race.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris CAN teach old dogs new tricks.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{9}
		\quotestart
		\quote{The only reason Thor is the god of lightning is because Chuck Norris stole his thunder.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{10}
		\quotestart
		\quote{Chuck Norris doesnt wear a watch. He decides what time it is.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris doesn't play Truth or Dare. He plays Truth or Death.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{12}
		\quotestart
		\quote{There is no Chuck Norris autographed memorabilia. Every time he's asked for a signature he just roundhouse kicks you.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{13}
		\quotestart
		\quote{Chuck Norris doesn't read books. He stares them down until he gets the information he wants.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{14}
		\quotestart
		\quote{Chuck Norris once forced a word to rhyme with "orange.".}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{15}
		\quotestart
		\quote{Chuck Norris came before the chicken and the egg}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris can delete the Recycling Bin.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{17}
		\quotestart
		\quote{Chuck Norris can Barbeque-under water.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can drift on a horse.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{19}
		\quotestart
		\quote{Chuck Norris does not need a bank card....He simply stares the bank machine down till he gets the money.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{20}
		\quotestart
		\quote{When Apollo was landing on the moon in 1968, Chuck Norris showed them where to park.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris has no middle name because nothing gets between Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{22}
		\quotestart
		\quote{The chief export of Chuck Norris is pain.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{23}
		\quotestart
		\quote{It is said that looking into Chuck Norris' eyes will reveal your future. Unfortunately, everybody's future is always the same: death by a roundhouse-kick to the face.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris''' house has no doors, only walls that he walks through.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{25}
		\quotestart
		\quote{When Chuck Norris gives you the peace sign, it is not a peace offering, it's the number of seconds you have to run.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{26}
		\quotestart
		\quote{If Superman and the Flash raced to the end of the universe who would win? Chuck Norris.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{27}
		\quotestart
		\quote{When Chuck Norris left for college he looked to his father Nd said "Youre the man of the house now".}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{28}
		\quotestart
		\quote{When Chuck Norris rides on a train, he can tell the driver where to go and let him off.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{29}
		\quotestart
		\quote{If you spell Chuck Norris wrong on Google it doesn't say, "Did you mean Chuck Norris?" It simply replies, "Run while you still have the chance."}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{30}
		\quotestart
		\quote{When life gave Chuck Norris lemons he round house kicked it in the face till it made the lemonade for him.}
		\endcal

		\begincal
		\monthtext{Oktober}
		\daytext{31}
		\quotestart
		\quote{Chuck Norris won the tour de france, on a stationary bike.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{1}
		\quotestart
		\quote{Chuck Norris invented airplanes because he go tired of being the only human to be able to fly.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{2}
		\quotestart
		\quote{Chuck Norris can create a rock so heavy that even he can't lift it. Then he lifts it just to show you who the hell Chuck Norris is.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris once kicked a ball so hard it broke the space time continuum, knocked out Amelia Eirhart, and sent her plane into the Pacific.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris once won a demolition derby without a car.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{5}
		\quotestart
		\quote{The Guinness Book of World Records was originally titled "Chuck Norris facts".}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{6}
		\quotestart
		\quote{Legend has it that a Nokia is indestructible. Legend also has it that Chuck Norris accidentally broke a Nokia with his pinky finger.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{7}
		\quotestart
		\quote{Chuck Norris is an incredible lawyer. He's won every case simply because you DON'T argue with Chuck Norris.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{8}
		\quotestart
		\quote{There are no laws of physics only laws of Chuck Norris. For example: The planets were created when Chuck Norris lifted the law on gravity and threw them in the air.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{9}
		\quotestart
		\quote{Chuck Norris can split a atom with his bare hands.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{10}
		\quotestart
		\quote{Chuck Norris can skip water across a rock.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{11}
		\quotestart
		\quote{Chuck Norris once gave a man the Hiemlich Manuever. That man still holds the record for most bones broken.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris' hands are protected under the 2nd Amendment.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{13}
		\quotestart
		\quote{Chuck Norris has to use oven mitts otherwise he'll burn the pans.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{14}
		\quotestart
		\quote{Chuck Norris once went to mars. Thats why there are no signs of life.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{15}
		\quotestart
		\quote{Chuck Norris can burn fire.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{16}
		\quotestart
		\quote{Chuck Norris was banned from skipping rocks after the tsunami in 2008.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{17}
		\quotestart
		\quote{Chuck Norris's Blood Type is AK-47.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can walk into your house and arrest you for trespassing.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{19}
		\quotestart
		\quote{If Chuck Norris owned a GPS, it would be asking him for directions.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{20}
		\quotestart
		\quote{Fool me once, shame on you. Fool Chuck Norris once and he will roundhouse you in the face.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris can capitalize numbers.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{22}
		\quotestart
		\quote{Chuck Norris ate a moose before he killed it.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{23}
		\quotestart
		\quote{FDR said "the only thing we have to fear is fear itself." The original words were "the only thing we have to fear is Chuck Norris," but he was too afraid to say it.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{24}
		\quotestart
		\quote{Champions are the breakfast of Chuck Norris.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{25}
		\quotestart
		\quote{Chuck Norris's words don't hurt.... they kill.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{26}
		\quotestart
		\quote{Chuck Norris wakes up in the middle of the night from nightmares about CHUCK Norris.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{27}
		\quotestart
		\quote{Chuck Norris' baby rattle is still shaking.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{28}
		\quotestart
		\quote{Before going up on stage, Chuck Norris breaks someone's leg to wish himself good luck.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{29}
		\quotestart
		\quote{Arnold Schwarzenegger is actually Chuck Norris' pinky finger.}
		\endcal

		\begincal
		\monthtext{November}
		\daytext{30}
		\quotestart
		\quote{Donald Trump can't fire Chuck Norris.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{1}
		\quotestart
		\quote{D-Day was Chuck Norris's Boy Scout Eagle project.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{2}
		\quotestart
		\quote{On a high school math test, Chuck Norris put down "Violence" as every one of the answers. He got an A+ on the test because Chuck Norris solves all his problems with Violence.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{3}
		\quotestart
		\quote{Chuck Norris had a pet rock.....He named it Earth.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{4}
		\quotestart
		\quote{Chuck Norris puts the "laughter" in "manslaughter".}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{5}
		\quotestart
		\quote{God is Chuck Norris' best friend.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{6}
		\quotestart
		\quote{Faster than a speeding bullet ... more powerful than a locomotive ... able to leap tall buildings in a single bound... yes, these are some of Chuck Norris's warm-up exercises.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{7}
		\quotestart
		\quote{If Chuck Norris tells you to "break a leg" and you don't, he'll do it for you.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{8}
		\quotestart
		\quote{Chuck Norris pitched a perfect game in baseball. From third base.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{9}
		\quotestart
		\quote{Chuck Norris once sold ebay, to ebay, on ebay.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{10}
		\quotestart
		\quote{Chuck Norris can tie his shoes with his feet.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{11}
		\quotestart
		\quote{Micheal Jackson can Moon Walk, but Chuck Norris can Sunrun.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{12}
		\quotestart
		\quote{Chuck Norris can see his forehead}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{13}
		\quotestart
		\quote{Everyone who thinks a cow jumping over a moon is a fairy tale has never seen Chuck Norris roundhouse kick a cow.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{14}
		\quotestart
		\quote{Did you ever hear the saying "This food isn't going to serve itself" Chuck Norris's food does.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{15}
		\quotestart
		\quote{Chuck Norris recorded the making of the first video camera.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{16}
		\quotestart
		\quote{Cyclones are the after effect left by the vortex of a Chuck Norris roundhouse kick. If you ever see a double cyclone, Chuck Norris is obviously giving someone a royal ass kicking!}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{17}
		\quotestart
		\quote{If you can't beat them, join them. Chuck Norris joins them, and then beats them.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{18}
		\quotestart
		\quote{Chuck Norris can play the note 'H' on the piano.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{19}
		\quotestart
		\quote{A toll booth pays Chuck Norris to pass.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{20}
		\quotestart
		\quote{Did you hear they renamed the show Fear Factor....It's now Chuck Norris.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{21}
		\quotestart
		\quote{Chuck Norris can sharpen his gun and reload his knife.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{22}
		\quotestart
		\quote{Chuck Norris doesn't bowl strikes, he just knocks down one pin and the other nine faint.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{23}
		\quotestart
		\quote{Jesus, Chuck Norris, and a Pope are stranded in the middle of the ocean in a boat. Jesus gets out and walks on the water to shore. Chuck Norris watches and does the same. The Pope tries and drowns. After seeing this, Jesus turns to Chuck Norris and says, "Do you think we should have told him about the rocks?" and Chuck Norris smiles and says, "What rocks?".}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{24}
		\quotestart
		\quote{Chuck Norris wrecked his bicycle and skinned the sidewalk with his knee.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{25}
		\quotestart
		\quote{When Chuck Norris goes jogging every morning he's actually maintaining earth rotation.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{26}
		\quotestart
		\quote{North Korea's borders are closed to prevent Chuck Norris from entering.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{27}
		\quotestart
		\quote{Chuck Norris's computer has no "backspace" button, Chuck Norris doesn't make mistakes.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{28}
		\quotestart
		\quote{Chuck Norris appears in all star wars movies. He is the Force.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{29}
		\quotestart
		\quote{Chuck Norris doesn't churn butter. He roundhouse kicks the cows and the butter comes straight out.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{30}
		\quotestart
		\quote{Chuck Norris can beat his reflection at rock paper scissors.}
		\endcal

		\begincal
		\monthtext{December}
		\daytext{31}
		\quotestart
		\quote{Chuck Norris can start a fire by staring at wood.}
		\vskip 4cm
		\quote{The end.}
		\endcal
